Evaluating the Supportive Effect of Feature Selection Methods on Machine Learning Models in Monitoring Forest Health Using Hyperspectral Remote Sensing Data

### 2020-04-05 docs/00-manuscripts/ieee/ieee-manuscript.tex
AB-review: opt method: index derivation

\noindent To account for geometric offsets (which were reported with up to 1 m from \ac{ICGC}) within the hyperspectral data, a buffer of two meters around the centroid of each tree was used during extraction of the reflectance values.
Subsequently, the value assigned to a tree observations was the mean of all pixels which were touched by the buffer drawn around each tree.
A pixel was considered to fall into a tree's buffer zone if the centroid of the respective pixel was touched by the buffer.
This is how the \texttt{extract()} function of the R package $\left\{raster\right\}$ handles buffer extraction.
In total, \(\frac{125*126}{2} = 7875\) NRIs were calculated.
Due to four corrupted bands of the sensor a total of 7471 indices were available for each observation.

>>>>

\noindent To account for geometric offsets (which were reported with up to 1 m from \ac{ICGC}) within the hyperspectral data, a buffer of two meters around the centroid of each tree was used for extraction of the reflectance values.
A pixel was considered to fall into a tree's buffer zone if the centroid of the respective pixel was touched by the buffer.
In total, \(\frac{121*122}{2} = 7471\) NRIs were calculated due to the first four bands of the sensor being corrupted.
